---
title: "Managing Project Files for Reproducibility"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      rows.print = 5)
```

## Pesky file locations 

--

* Importing data, graphics, and other information into R Markdown or R script files requires specifying the location where the data, graphics, or other files are kept

--

* One way to specify the location is to use a local file path to give the exact location of the data, graphics, or other information  

--

* Another way to specify location is to use the `setwd()` function to specify an *absolute* file path as the location where R should look for files 

--

* Both of these methods are problematic since they can easily break and are not useful to collaborators 

--

* Instead, using R Project files and the `here` package solve these problems by linking together your files and making file paths relative

---

## R Projects for reproducibility

--

* An R Project file can be added to a local folder and will show up in the folder with an `.Rproj` file extension 

--

* When an `.Rproj` file is opened, the project directory becomes the working directory

--

* R Markdown and Source files in the folder with the R project file can import data and other files using the location of the file relative to the working directory

--

* For simple project with a few files, adding and R project file is all you need

---

## The here package for reproducibility

--

* Large R projects that contain multiple subfolders make even relative file paths challenging 


--

* For these projects, the `here` package is a useful tool 

--

* The `here` package creates file paths relative to the working directory of the project 


---

## Using the here package

--

* After installing and opening the `here` package, use `i_am()` and specify a file path for the current file that is relative to the project main directory (the place you stored your `.Rproj` file) 

--

* After using `i_am()` in a file, use the `here()` function to specify file locations relative to the project main directory

--

* This is most useful when data and other files are in subfolders of the main directory; when everything is in the same folder, it seems unnecessary 

--

* For example, if a csv data file called projectdata.csv were in a subfolder of the main project folder with the subfolder named "datafiles," the here function would build the location of the data like this: 

```{r}
data <- read_csv(here("datafiles", "projectdata.csv"))
```


---

class: my-turn, center, middle

# Demo

```{r echo = FALSE}
# add an R Project file and the here package to the demo
# suggest to the audience they could follow along
```


