---
title: "Reproducibility for the Rest of Us"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      rows.print = 5)
```

## Lesson 10: Embedding files to improve reproducibility

* To reproduce analyses, the data and the code (or very detailed instructions for analysis) are the necessary components

* One way to include everything needed for reproducing analyses is embedding the data, code, and instructions in Quarto html rendered files

    + The `xfun` package is used to embed files

---

## Using the `xfun` package

* The `xfun` package can be used to attach a single file, multiple files, or a directory in a knit html document

* When multiple files are attached, they are compressed into a zip file, which is embedded

* The file, files, or directory is available by clicking on a link in the knit html file


---

## Demo of the `xfun` package

```{r echo = FALSE}
# demo the xfun package and .Rproj on the Quarto file
# suggest to the audience they could follow along
```

---

## Resources

* [xfun](https://cran.r-project.org/web/packages/xfun/index.html) package documentation
* [Using RMarkdown to Create Reproducible Documents](https://www.youtube.com/watch?v=z2a80FnLFfE&t=98s) with Mine Çetinkaya-Rundel
    