---
title: "Prologs & Annotation"
output:
  xaringan::moon_reader:
    css: ["css/style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      rows.print = 5)
```

##  What are prologs & annotation?

--

* Prologs and annotation add text to your code file to help others understand the code

--

* A prolog describes the code purpose, the location of files, the file author, and anything else important to understanding why the code exists and how to use it

--

* Annotation, or commenting, is providing descriptions of the purpose or function of specific code within the code file 

--

* There are recommended ways of writing a prolog and annotation that will improve the quality and reproducibility of your work

---

## Prologs

--

* A prolog is information added (usually as comments or annotation) at the top of a code file to provide information about the contents of the file

--

* A prolog can include:

    + Project name
    
    + Project purpose
    
    + Name and location of any data sets used in the code
    
    + Name of code author
    
    + Date the code was created
    
    + Date the code was last edited 


---


## Shorter prologs

* For some projects, a short informal prolog is sufficient

```{r}
####################################
# Project name
# Project purpose
# Code author name
# Date last edited
# Location of data used
####################################

```


---

## Longer prologs

```{r}
# PROLOG ################################################################
# PROJECT:NAME OF PROJECT HERE #
# PURPOSE:MAJOR POINT(S) OF WHAT I AM DOING WITH THE DATA HERE #
# DIR:
# DATA: 
# list directory(-ies) for files here 
# list data set file names/availability here, e.g., 
# filename.correctextension 
# somewebaddress.com 
# AUTHOR NAME(S) 
# AUTHOR:
# CREATED: MONTH dd, YEAR 
# LATEST:  MONTH dd, YEAR
# NOTES:  indent all additional lines under each heading, #
#         & use the hashmark bookends that appear #
#         KEEP PURPOSE, AUTHOR, CREATED & LATEST ENTRIES IN UPPER CASE, #
#         with appropriate case for DIR & DATA, lower case for notes #
#         If multiple lines become too much, #
#         simplify and write code book and readme. #
# PROLOG         ######################################################
```

    
---

## Annotating your code 

--

* Annotation is a set of comments that explain something about your code 

--

* Annotation should give the reason for the code (not describe what it does)

--

* Comments are written within a code chunk or script file using a # at the beginning of the line

--

* Annotation can make work **less reproducible** if it is not updated

--

* Use annotation sparingly to clarify!

---

## Example of annotation

* It is difficult to know, without running this code, what this figure will be:

```{r eval = FALSE}
globalData2019clean %>% 
  ggplot(aes(x = AGE)) +
  geom_histogram(color = "white") +
  facet_wrap(facets = vars(country)) +
  labs(x = "Age in years", 
       caption = "Data source: Pew Research Center Global Attitudes Survey (2019)") +
  theme_bw(base_size = 14, base_family = "serif")
```


--

* A simple statement can help:

```{r eval = FALSE}
# distribution of age by country using histograms
globalData2019clean %>% 
  ggplot(aes(x = AGE)) +
  geom_histogram(color = "white") +
  facet_wrap(facets = vars(country)) +
  labs(x = "Age in years", 
       caption = "Data source: Pew Research Center Global Attitudes Survey (2019)") +
  theme_bw(base_size = 14, base_family = "serif")
```

---

class: my-turn, center, middle

# Demo

```{r echo = FALSE}
# add some annotation and start a prolog in the participant file
```

---

class: inverse

## Your Turn

* Open the participant `unformatted-r-code.R` file and complete the prolog

* Add annotation where needed in the file

