---
title: "Reproducible Research Example"
format: html
editor: visual
bibliography: references.bib
---

```{r}
#| echo: false
#| warning: false
#| message: false
library(package = "tidyverse")
library(package = "haven")
library(package = "table1")
library(package = "finalfit")
library(package = "knitr")
library(package = "xfun")
library(package = "here")
```

### Project description

Using the **2019 Global Attitudes & Trends** data set from the **Pew Internet & American Life** website, I will answer the research question, *Do perceptions about various U.S. policies under President Trump vary by country?*

The data and code book are available on the Pew website (need free account).

```{r}
#| echo: false

xfun::embed_files(c("Formatted-reproducible-project.qmd","datafiles/Pew Research Center 2019 Global Attitudes Survey WEB .docx","datafiles/Pew Research Center Global Attitudes Spring 2019 Dataset WEB.sav","references.bib"), text = "Download data, code, codebook, and text here.")
```

### Measurement

To answer my research question, I used a subset of the data that included survey participants responses to the following questions: *As I read some policies of U.S. President Donald Trump, please tell me if you approve or disapprove of each one. How about \[INSERT ITEM\]?*

+----------------------------------------------------------------------------------------------------+-----------------------------+
| Items                                                                                              | Response options            |
+====================================================================================================+=============================+
| U.S. withdrawal from international climate change agreements                                       | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+
| Building a wall on the border between the U.S. and Mexico                                          | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+
| U.S. withdrawal from the Iran nuclear weapons agreement                                            | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+
| Allowing fewer immigrants into the U.S.                                                            | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+
| U.S. increasing tariffs or fees on imported goods from other countries                             | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+
| U.S. negotiations with North Korean leader Kim Jong-Un about the country's nuclear weapons program | 1 = Approve\                |
|                                                                                                    | 2 = Disapprove\             |
|                                                                                                    | 8 = Don't know\             |
|                                                                                                    | 9 = Refused                 |
+----------------------------------------------------------------------------------------------------+-----------------------------+

This paragraph might talk about about the process and statistical methods used. What happened during data management (recoding, missing value handling), which descriptive statistics and statistical tests were used, what assumptions were checked.

```{r}
#| echo: false
#| results: false
#| warning: false
#| message: false

# define where this file is relative to the project root
i_am("Formatted-reproducible-project.qmd")

# import 2019 Pew data on global policy attitudes
globalData2019 <- read_spss(here("datafiles", "Pew Research Center Global Attitudes Spring 2019 Dataset WEB.sav"))

# sample 10,000 from the Pew file
set.seed(seed = 42)
globalData2019samp <- sample_n(globalData2019, 10000)

# function to recode policy items
recode_policy_items <- function(item) {
  recode_factor(item,
      '1' = 'Approve',
      '2' = 'Disapprove',
      '8' = NA_character_,
      '9' = NA_character_)
}

# select countries of interest and clean data
globalData2019clean <- globalData2019samp %>%
  filter(country %in% c(3, 5, 15, 19, 21, 22, 27, 34)) %>%
  select(country, POLICY_CLIMATE, POLICY_THEWALL, 
         POLICY_NUCLEAR, POLICY_IMMIG, 
         POLICY_TARIFF, POLICY_NORTHKOREA) %>%
  zap_labels() %>%
  mutate_at(vars(matches('POLICY')), recode_policy_items) %>% 
  mutate(country = recode_factor(country, 
                                 "3" = "Brazil", 
                                 "5" = "Canada", 
                                 "15" = "Japan", 
                                 "19" = "Mexico", 
                                 "21" = "Nigeria", 
                                 "22" = "Phillippines", 
                                 "27" = "South Korea", 
                                 "34" = "United States")) 

# check recoding
summary(object = "globalData2019clean")
```

### Results

Here is a table showing the basic descriptive statistics.

##### Table. Policy support for Trump policies among 10,000 survey participants in Brazil, Canada, Japan, Mexico, Nigeria, Philippines, South Korea, United States. (Data source: Pew Research Center Global Attitudes Survey (2019)).

```{r}
#| echo: false
#| message: false

# add labels for table
label(globalData2019clean$country) <- 
  "Country"
label(globalData2019clean$POLICY_CLIMATE) <- 
  "U.S. withdrawal from international climate change agreements"
label(globalData2019clean$POLICY_THEWALL) <- 
  "Building a wall on the border between the U.S. and Mexico"
label(globalData2019clean$POLICY_NUCLEAR) <- 
  "U.S. withdrawal from the Iran nuclear weapons agreement"
label(globalData2019clean$POLICY_IMMIG) <- 
  "Allowing fewer immigrants into the U.S."
label(globalData2019clean$POLICY_TARIFF) <- 
  "U.S. increasing tariffs or fees on imported goods from other countries"
label(globalData2019clean$POLICY_NORTHKOREA) <- 
  "U.S. negotiations with North Korean leader Kim Jong-Un about the country’s nuclear weapons program"

# create table
tableDesc <- globalData2019clean %>% 
  summary_factorlist(explanatory = c("POLICY_CLIMATE", 
                                     "POLICY_THEWALL", 
                                     "POLICY_NUCLEAR", 
                                     "POLICY_IMMIG", 
                                     "POLICY_TARIFF", 
                                     "POLICY_NORTHKOREA"))
kable(tableDesc, 
      row.names = FALSE, 
      col.names = c("Characteristic", "Category", "n (%)    "), 
      align = c("l", "l", "r"))
```

Maybe add some text here pointing out anything interesting or unexpected in the table that the readers might want to view more closely. Also explain anything in the table that suggests how the research question might eventually be answered.

### Visualizing the relationships between country and policies

##### Figure. Percent approving or disapproving of the policy of U.S. withdrawal from international climate change agreements by country.

```{r}
#| echo: false

# create figures
globalData2019clean %>%
  drop_na(POLICY_CLIMATE) %>%
  group_by(country, POLICY_CLIMATE) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_CLIMATE)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "U.S. withdrawal\nclimate\nagreement", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif")
```

##### Figure. Percent approving or disapproving of the policy of building a wall on the border between the U.S. and Mexico by country.

```{r}
#| echo: false

globalData2019clean %>%
  drop_na(POLICY_THEWALL) %>%
  group_by(country, POLICY_THEWALL) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_THEWALL)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "Build wall\nbetween U.S.\nand Mexico", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif") 
```

##### Figure. Percent approving or disapproving of the policy of U.S. withdrawal from the Iran nuclear weapons agreement by country.

```{r}
#| echo: false

globalData2019clean %>%
  drop_na(POLICY_NUCLEAR) %>%
  group_by(country, POLICY_NUCLEAR) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_NUCLEAR)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "U.S. withdrawal\nIran\nagreement", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif")
```

##### Figure. Percent approving or disapproving of the policy of allowing fewer immigrants into the U.S. by country.

```{r}
#| echo: false

globalData2019clean %>%
  drop_na(POLICY_IMMIG) %>%
  group_by(country, POLICY_IMMIG) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_IMMIG)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "Fewer immigrants\nallowed in U.S.", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif")
```

##### Figure. Percent approving or disapproving of the policy of U.S. increasing tariffs or fees on imported goods from other countries by country.

```{r}
#| echo: false

globalData2019clean %>%
  drop_na(POLICY_TARIFF) %>%
  group_by(country, POLICY_TARIFF) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_TARIFF)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "U.S. increase\nimport tarrifs", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif")
```

##### Figure. Percent approving or disapproving of the policy of U.S. negotiations with North Korean leader Kim Jong-Un about the country's nuclear weapons program.

```{r}
#| echo: false

globalData2019clean %>%
  drop_na(POLICY_NORTHKOREA) %>%
  group_by(country, POLICY_NORTHKOREA) %>%
  count() %>%
  group_by(country) %>%
  mutate(percCo = 100 * (n / sum(n))) %>%
  ggplot(aes(x = country, y = percCo, fill = POLICY_NORTHKOREA)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(caption = "Data source: Pew Research Center Global Attitudes Survey (2019)", fill = "U.S. nuclear\nnegotiations with\nNorth Korea", y = "Percent in Country") +
  theme_bw(base_size = 10, base_family = "serif")
```

### Discussion

After all the methods and results, you would usually summarize the key points from your analyses and add some context by connecting your results to published evidence relevant to your work. Here is where you might add citations. More discussion of the findings that cite some of the literature in this area [@Kolencik2022]. Another statement about the literature and citing it goes here [@Sully2022].

### References
